### 2022-03-31 Notes/overview.tex

One important feature is,
\begin{equation}
\lim_{r \rightarrow 0}\sigma_{GBWBK} \simeq  -\frac{\pi^2 r^2\alpha_s(\mu^2) x g(x,\mu^2)}{3},
\end{equation}
where $g(x,\mu^2)$ is integrated gluon density. This is the limit $r \rightarrow 0$ of \hyperlink{ugd}{ $\sigma_{dp}$ in terms of unintegrated gluon density}.

@@

@@

Unintegrated gluon density\hypertarget{ugd}{$f(x,k^2)$} is related to the dipole cross section $\sigma_{dp}$ by% the fourier trransform
\cite{gbk2002}\cite{nikolaev1994}:

\begin{equation}
\sigma_{dp}=\frac{2 \pi}{3} \int\frac{d^2 \mathbf{k}}{k^4} \alpha_s f(x,k^2) \left(1-e^{i \pairdot{k}{r}}\right).
\end{equation}

and hence the fourier transform
\begin{align}
\nabla^2_{\mathbf{r}} \sigma_{dp}&=\frac{2 \pi}{3} \int\frac{d^2 \mathbf{k}}{k^2} \alpha_s f(x,k^2)  e^{i \pairdot{k}{r}}
\end{align}

unintegrated gluon density $f(x,k^2)$ is related to the integrated gluon density $g(x,Q^2)$ by 
 \begin{equation}
x g (x,Q^2)=\int f(x,k^2)d k^2 \theta(Q^2-k^2)/k^2.
\end{equation}

>>>>

One important feature is,
\begin{equation}
\lim_{r \rightarrow 0}\sigma_{GBWBK} \simeq  \frac{\pi^2 r^2\alpha_s(\mu^2) x g(x,\mu^2)}{3},
\end{equation}
where $g(x,\mu^2)$ is integrated gluon density. This is the limit $r \rightarrow 0$ of \hyperlink{ugd}{ $\sigma_{dp}$ in terms of unintegrated gluon density}.

The scale is proposed to be $\mu^2=\frac{C}{r^2}+{\mu^2_0}$.

@@

$k_g$ transverse momentum of gluon.\\
$k_q$ transverse momentum of quark.\\
$r$  dipole size.\\
dipole scattering amplitude dissapears
 for $r=0$ (cf. color trnsparency), and saturates to a constant for large $r$. cf.\cite{gbw1998}.

@@

Unintegrated gluon density\hypertarget{ugd}{$f(x,k^2)$} is related to the dipole cross section $\sigma_{dp}$ by% the fourier trransform
\cite{gbk2002, nikolaev1994, nikolaev2001}:

\begin{equation}
\sigma_{dp}=\frac{2 \pi}{3} \int\frac{d^2 \mathbf{k_g}}{k_g^4} \alpha_s f(x,k_g^2) \left(1-e^{i \pairdot{k_g}{r}}\right).
\end{equation}

and hence the fourier transform
\begin{align}
\nabla^2_{\mathbf{r}} \sigma_{dp}&=\frac{2 \pi}{3} \int\frac{d^2 \mathbf{k_g}}{k_g^2} \alpha_s f(x,k_g^2)  e^{i \pairdot{k_g}{r}}.
\end{align}

In the small $r$ limit\cite{nikolaev2001}, 
\begin{equation}
\sigma_{dp}(x,r)=\frac{\pi^2 r^2\alpha_s(\mu^2=\frac{C}{r^2}) x g(x,\mu^2=\frac{C}{r^2})}{3}.
\end{equation}

unintegrated gluon density $f(x,k_g^2)$ is related to the integrated gluon density $g(x,Q^2)$ by 
 \begin{equation}
x g (x,Q^2)=\int d k_g^2 f(x,k_g^2) \theta(Q^2-k_g^2)/k_g^2.
\end{equation}
